### 2017-11-30 manuscript.rmd
added VARS ref n the methods
added VARS ref

Siphonophores (Fig. 1) are among the most abundant gelatinous predators in the open ocean, and play an important ecological role in oceanic waters [@pugh1984diel;@pugh1997vertical; @williams1981vertical;@purcell1981dietary;@pages2001gelatinous]. Siphonophores, which belong to Hydrozoa (Cnidaria), are found at all depths in the ocean. *Physalia physalis*, the Portuguese man of war, floats at the surface and, as a result, is the most familiar siphonophore species. Most siphonophores species are planktonic, living in the midwater where some grow to be longer than 30 meters in length. There is also a small clade of benthic siphonophores, the Rhodaliidae [@carre1995ordre;@Totton1960;@pugh1983benthic], that are tethered to the bottom for part of their lives. In all, there are currently 188 valid described species.

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years (XXX) due to their very unique structure and development. Like many other cnidarians, they are colonial -- they grow by incomplete asexual reproduction. Each siphonophore colony arises from a single embryo that forms the protozooid, the first body. A growth zone then arises that asexually produces other genetically identical zooids [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animals, but are physiologically integrated [@totton1965synopsis; @mackie1988siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial animals in terms of colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. Each zooid is functionally specialized for a particular task (e.g feeding, reproducing, swimming) (fig. 2) [@dunn2006evolution], and they are arranged in a repeating species-specific pattern.

@@

Morphological character data used in trait mapping were obtained from the literature, or from direct observation of available voucher material. We used stochastic character mapping to infer the probable evolution of traits on the tree in R using the `phytools` package [@MEE3:MEE3169, @huelsenbeck2003stochastic].  Subsequent analyses were conducted in R and integrated into this manuscript with the `knitr` package. See Supplementary Information for R package version numbers.

@@

In this phylogeny, *Physophora gilmeri* along with *Lychnagalma utricularia* (both not included in previous phylogeny) are sister to the Agalmatidae *sensu stricto*, a clade restricted to *Agalma*, the Athorybiidae,*Halistemma* and *Nanomia* [@Dunn:2005dy]. In the rDNA study, *Physophora hydrostatica* was sister to the Forskaliidae with low support. *Cordagalma cordiforme* (= *Cordagalma ordinatum* [@pugh2016synopsis]) was previously unresolved, while in this analysis *Cordagalma* sp is in a clade with *Forskalia asymmetrica*, falling outside of the Agalmatidae *sensu stricto*. *Cordagalma* has traditionally been placed within the Agalmatidae *sensu lato* [@totton1965synopsis], although the Agalmatidae is considered to be a catch-all family in need of revision [@pugh2006taxonomic,@pugh1998re, @Dunn:2005dy].

>>>>

Siphonophores (Fig. 1) are among the most abundant gelatinous predators in the open ocean, and play an important ecological role in oceanic waters [@pugh1984diel;@pugh1997vertical; @williams1981vertical;@purcell1981dietary;@pages2001gelatinous]. Siphonophores, which belong to Hydrozoa (Cnidaria), are found at all depths in the ocean. *Physalia physalis*, the Portuguese man of war, floats at the surface and, as a result, is the most familiar siphonophore species[@Totton1960]. Most siphonophores species are planktonic, living in the midwater where some grow to be longer than 30 meters in length. There is also a small clade of benthic siphonophores, the Rhodaliidae [@pugh1983benthic], that are tethered to the bottom for part of their lives. In all, there are currently 188 valid described species.

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years due to their very unique structure and development [@mapstone2014global;]. Like many other cnidarians, they are colonial -- they grow by incomplete asexual reproduction. Each siphonophore colony arises from a single embryo that forms the protozooid, the first body. A growth zone then arises that asexually produces other genetically identical zooids [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animals, but are physiologically integrated [@totton1965synopsis; @mackie1988siphonophore; @dunn2006evolution]. Siphonophores differ significantly from all other colonial animals in terms of colony structure, development, and the degree to which they are functionally specialized [@Beklemishev1969;@cartwright2010character]. Each zooid is functionally specialized for a particular task (e.g feeding, reproducing, swimming) (fig. 2) [@dunn2006evolution], and they are arranged in a repeating species-specific pattern.

@@

Morphological character data used in trait mapping were obtained from the literature, or from direct observation of available voucher material. Depth distribution data was queried from the MBARI VARS ( http://www.mbari.org/products/research-software/video-annotation-and-reference-system-vars/, [@schlining2006mbari]) database (with assistance and permission from SHD Haddock), including records from several MBARI cruises. We used stochastic character mapping to infer the probable evolution of traits on the tree in R using the `phytools` package [@MEE3:MEE3169, @huelsenbeck2003stochastic]. Subsequent analyses were conducted in R and integrated into this manuscript with the `knitr` package. See Supplementary Information for R package version numbers.

@@

In this phylogeny, *Physophora gilmeri* along with *Lychnagalma utricularia* (both not included in previous phylogeny) are sister to the Agalmatidae *sensu stricto*, a clade restricted to *Agalma*, the Athorybiidae,*Halistemma* and *Nanomia* [@Dunn:2005dy]. In the rDNA study, *Physophora hydrostatica* (sister species to *P. gilmeri*) was sister to the Forskaliidae with low support. *Cordagalma cordiforme* (= *Cordagalma ordinatum*)[@pugh2016synopsis] was previously unresolved, while in this analysis *Cordagalma* sp is in a clade with *Forskalia asymmetrica*, falling outside of the Agalmatidae *sensu stricto*. *Cordagalma* has traditionally been placed within the Agalmatidae *sensu lato* [@totton1965synopsis], although the Agalmatidae is considered to be a catch-all family in need of revision [@pugh2006taxonomic,@pugh1998re, @Dunn:2005dy].
